Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2022-12-14 docs/manuscript/manuscript.tex
Results - Tables Update 1

\subsection*{Survey Demographics}
A total of \textit{n}=215 of the authors we contacted completed the online survey with information sufficient for analysis. The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. The refusal rate was 3.1 percent.\endnote{All outcome rates are reported using \citet{aaporstandards} standards. The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.} 
ADD COMPARISON TO SAMPLE FRAME.

\subsection*{PCAish Summary Across Dimensions}
This subsection will pivot on Table 9 that has rows representing PCA-like aggregate measures of 1) definition, 2) Familiarity 3)practice, 4) Barriers and two groups of rows (Quant, Qual, Mixed) and (Human, Physical, GIS/Methods, NS).

\subsubsection*{Definition of Reproducibility}
Definition Questions and Q8 about beliefs about the interpretation for reproductions. Dig into those respondents that had variations in beliefs on Q8 sequence. Q17 about importance of reproduction. Close with Q13.

>>>>

\subsection*{Survey Demographics}
A total of \textit{n}=215 of the authors we contacted completed the online survey with information sufficient for analysis. The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. The refusal rate was 3.1 percent.\endnote{All outcome rates are reported using \citet{aaporstandards} standards. The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}

\begin{itemize}
    \item Include a comparison of sample to the sample frame along the dimensions available from the frame. (Table 0)
    \item Include a summary of the key in sample characteristics (Table 1?). Rows - Title, Citations (pulled from frame), Gender; cols - methods and subfields. \textcolor{red}{Does this need to be a table? I am not sure any of these demographics really matter to our analysis. That is unless we plan to look at some measure across seniority or 'impact', which we could do.}
\end{itemize}

\subsection*{Aggregate Measures Along 4-Dimensions}
This subsection will pivot on Table 9 that has rows representing aggregate measures of 1) definition, 2) Familiarity 3) Experience, 4) Barriers and two groups of columns representing (Quant, Qual, Mixed) and (Human, Physical, GIS/Methods, NS).

\begin{itemize}
    \item Overall story is that collectively geographers are aware of reproducible research practices, but don't have a matching amount of direct experience using those practices. There are also many perceived barriers to conducting reproducible research.
    \item High - Low gradient across all aggregate measures from Quant-MM-Qual.
    \item High - Low familiarity gradient Method-Physs-NS-H
    \item Likely need to comment on survey including many reproducible research practices that center on, or are easier to accomplish with, when using quantitative data and methods. This reality may automatically deflate the aggregate measures of certain sub-group. We can use the response to Q8f as a filter to explore this issue. \textcolor{red}{For conclusions - Points to the emphasis on quantitative, particularly computational, focus in the reproducibility literature. Suggests a meed to examine what reproducibility means in the context of geography's qual, NS, and human traditions.} 
\end{itemize}

\subsubsection*{Definition of Reproducibility}
\begin{itemize}
    \item Self-reported definition (Q6) analysis.
    \item Interpretations of reproductions (Q8) - focus on Q8a, Q8b, Q8e as these provide the most direct information about how a respondent processes the evidence provided by a reproduction. Match Q8e with 17c, 17e, 17f which are importance questions about credibility. Match Q8b with 17a which are both about validity. 
    \item Importance of reproducibility (Q17) - Reproducibility was/wasn't seen as important for other goals - error reduction (17b), effort duplication (17d), scientific communication (17g, 17h), training (17i, 8d).
    \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
\end{itemize}
